Procurement Dynamics: Analyzing Federal Contract Awards to Microsoft

### 2024-11-26 paper/paper.qmd
Update README.md and paper

```{r}
#| label: fig-preparatory
#| fig-cap: The histogram shows the distribution of preparatory period, which demonstrates the days between start and awarded date.
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| label: fig-contract
#| fig-cap: The histogram shows the distribution of performance period, which demonstrates the days between start and end date. The right skewed distribution indicates that the majority of contract duration is within a year.
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

@@

+ Model Justification

@@

## Model Validation

@@

```{r}
#| label: fig-mobilization
#| fig-cap: The scatter plot shows the distribution of performance period, which demonstrates the days between start and end date. The right skewed distribution indicates that the majority of contract duration is within a year. An over 5 years performance period implies a massive project that requires extensive preparation.
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| 
ggplot(data, aes(x = AwardDate, y = StartDate)) +
  geom_point(aes(color = Contract)) +
  labs(x = "Award Date", y = "Start Date", title = "Award Date vs Start Date") +
  theme(legend.position = "none")  # This removes the legend
```

```{r}
#| label: fig-performance
#| fig-cap: The scatter plot shows the distribution of performance period, which demonstrates the days between start and end date. The right skewed distribution indicates that the majority of contract duration is within a year. An over 5 years performance period implies a massive project that requires extensive preparation.
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| 
ggplot(data, aes(x = StartDate, y = EndDate)) +
  geom_point(aes(color = Contract)) +
  labs(x = "Start Date", y = "End Date", title = "Start Date vs End Date") +
  theme(legend.position = "none")  # This removes the legend
```

@@

## Additional Tables & Figures

>>>>

```{r}
#| label: fig-preparatory
#| fig-cap: The histogram shows the distribution of preparatory period.
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.width: 4    # Width of the figure in inches
#| fig.height: 3   # Height of the figure in inches

@@

```{r}
#| label: fig-contract
#| fig-cap: The histogram shows the distribution of performance period, which demonstrates the days between start and end date.
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

To understand the factors influencing the amount of federal procurement contracts awarded to Microsoft. I construct a linear regression model to explains variations in contract values.

@@

This paper utilizes a linear regression model to examine the relationships between the dependent variable.

$$Amount = \beta_0 + \beta_1 Contract + \beta_2 Buyer + \beta_3 ContractDays + \beta_4 PhaseDays + \epsilon$$
As defined in [@sec-data], each predictor variable has been chosen to reflect characteristics that influence the contract amount.

@@

The model takes several assumptions, including the relationship between the predictors and the outcome is linear, each contract is independent, the variance of the error term is constant, and predictor variables are not highly correlated with each other.

While the model presented offers valuable insights into the dynamics of Microsoft’s federal procurement contracts, there are some limitations including categorization of contract types, generalizability, data quality, potential for endogeneity, and unobserved variables. These limitations will be discussed in [@sec-discussion].

## Model Validation?

R-squared, adjusted R-squared

tests (e.g. VIF, AIC, BIC).

@@

```{r}
#| label: fig-mobilization
#| fig-cap: The scatter plot shows ...
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| 
ggplot(data, aes(x = AwardDate, y = StartDate)) +
  geom_point(aes(color = Contract)) +
  labs(x = "Award Date", y = "Start Date", title = "Award Date vs Start Date") +
  theme(legend.position = "none")  # This removes the legend
```

```{r}
#| label: fig-performance
#| fig-cap: The scatter plot shows ....
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| 
ggplot(data, aes(x = StartDate, y = EndDate)) +
  geom_point(aes(color = Contract)) +
  labs(x = "Start Date", y = "End Date", title = "Start Date vs End Date") +
  theme(legend.position = "none")  # This removes the legend
```

@@
